{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-03 Paper/main.tex
merging files to pull changes

	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature. Although classical statistical methods can often process this data, but only FDA allows extracting the information given by the smoothness of the underlying process of the functional data (cf. \cite{levitin_introduction_2007}).
	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).

@@

	\section{Theory}
	In multivariate regression, data is often observed in the form of elements from Euclidean space, $\mathbb{R}^p$. However, the statistics derived from infinite-dimensional random functions cannot be defined on a finite dimensional space. To understand functional linear regression and the differences between the methods presented in this paper, it is therefore necessary to introduce some concepts and extend known aspects of linear regression theory to include functional objects. One integral concept in inferential statistics are random variables. Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.\\
	A typical case known to every undergraduate student of economics in less formal detail is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers. As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space. A formalization of this idea makes some more theoretical considerations necessary. The following theoretical introduction closely follows chapters 2.3 and 2.4 from \cite{hsing_theoretical_2015}.

@@

		where $Z \sim \mathcal{N}(0,1)$. In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses. These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic bspline basis-function $\{5,6,...,18\}$ and fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
		 To obtain valid out of sample properties for the FPCR, within each of the ten 10 fold cross-validation splits, we first calculate the Functional Principal Components of the trainig-set $\mathcal{T}$ for each curve. These scores are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation:

		 {\color{orange}I guess we don't use the scores of the training set to estimate scores of test set but eigenfunction of traningset..}
		 {\color{blue} We should mention how we derived the original principal components. (bspline basis and number of basis functions and harmonics.) As we chose a high number for both to capture all features of the data set. As we explain the approximations for the estimation, this question could come up, so we have to make it specific.}

	\begin{equation}
		\begin{split}
			\hat{\xi}_{i}^{m, \mathcal{H}} &=  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
						    = \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^{m, \mathcal{T}} \psi_{k}(s)\right)} \mathrm{d}s \\
			 &= \sum_{j \in \mathcal{I}} \left[ a_{i,j}^{\mathcal{H}}\sum_{k \in \mathcal{L}}  b_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
		\end{split}
	\end{equation}
	\vspace{	0.2cm}

@@

	\paragraph{Monomial Basis}
	Due to the high collinearity of these basis{(\color{orange} How about stressing the higher order? Are they already highly correlated at lower orders?)}, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant. For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$ and show a better performance than bsplines for this coefficient function, but show the weakest performance for the coefficient function $f_2$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios. This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2, Y_2$ this weakness is still visible, but less strongly pronounced.

>>>>

	\begin{itemize}
		\item Describe the idea of regressing a scalar on functional data
		\item Describing the difference to multiple linear regression intuitively
		\item Giving an intuitive example
	\end{itemize}	
	Functional Data Analysis (FDA) is {\color{red} (roots in the 1940s Grenander and Karhunen)} gaining more attention as researchers from different fields collect data that is functional in nature. Although classical statistical methods can often process this data, but only FDA allows extracting the information given by the smoothness of the underlying process of the functional data (cf. \cite{levitin_introduction_2007}).
	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).

@@

	\section{Theory}
	In multivariate regression, data is often observed in the form of elements from the Euclidean space, $\mathbb{R}^p$. To understand functional linear regression and the differences between the methods presented in this paper, it is therefore necessary to introduce some concepts and extend known aspects of linear regression theory to include functional objects. One integral concept in inferential statistics are random variables. Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space.\\
	A typical case known to every undergraduate student of economics in less formal detail is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers. As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space. However, the statistics derived from infinite-dimensional random functions cannot be defined on a finite dimensional space. A formalization of this idea makes some more theoretical considerations necessary. The following theoretical introduction closely follows chapters 2.3 and 2.4 from \cite{hsing_theoretical_2015}.

@@

		where $Z \sim \mathcal{N}(0,1)$. In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses. These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic bspline basis-function $\{5,6,...,18\}$ and fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
		 To obtain valid out of sample properties for the FPCR, within each of the ten 10 fold cross-validation splits, we first calculate the first $nharm$ FPC´s for $nharm \in \{2,3,4\}$ of the trainig-set $\mathcal{T}$ for each curve $i \in \{1,2, \dots, 200\}$, which was smoothed with the respective basis function specification. The obtained eigenfunctions $\nu^{m,\mathcal{T}}$ are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation

		 {\color{orange}I guess we don't use the scores of the training set to estimate scores of test set but eigenfunction of traningset..}{\color{green} Adressed }
		 {\color{blue} We should mention how we derived the original principal components. (bspline basis and number of basis functions and harmonics.) As we chose a high number for both to capture all features of the data set. As we explain the approximations for the estimation, this question could come up, so we have to make it specific. }{\color{green} Adressed }

	\begin{equation}
		\begin{split}
			\hat{\xi}_{i}^{m, \mathcal{H}} &=  \int_{0}^{1} {\color{red} \left(X_{i}^{\mathcal{H}}(s) - \hat{\mu}^{\mathcal{T}}(s)\right)} {\color{blue}\hat{\nu}^{m, \mathcal{T}} }\mathrm{d}s) 
						    = \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j}^{\mathcal{H}} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^{m, \mathcal{T}} \psi_{k}(s)\right)} \mathrm{d}s \\
			 &= \sum_{j \in \mathcal{I}} \left[ a_{i,j}^{\mathcal{H}}\sum_{k \in \mathcal{L}}  b_{k}^{m, \mathcal{T}} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s\right]
		\end{split}
	\end{equation}
	with truncation parameter $m$.
	\vspace{	0.2cm}

@@

	\paragraph{Monomial Basis}
	Due to the in the number of basis functions increasing collinearity of these basis{(\color{orange} How about stressing the higher order? Are they already highly correlated at lower orders?)}{\color{green} Adressed }, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant. For reasons outlined in {\color{green} Link chapter}, they seem suited for $f_1$ and show a better performance than bsplines for this coefficient function, but show the weakest performance for the coefficient function $f_2$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios. This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2, Y_2$ this weakness is still visible, but less strongly pronounced.
